---
title: "MADRID GROUP"
author: "BUSINESS TRAVEL"
date: '28&30 September, 2019'
output:
 
  html_document:
    css: FORMATO.css
    highlight: textmate
    theme: cosmo
    toc: yes
    toc_float: yes
---

<script> 
    $(document).ready(function() { 
    $head = $('#header'); 
    $head.prepend('<A href = https://www.cuttingedge-events.com><img src ="LOGO.png" width="150" vspace="50" align="right"></A>') 
    }); 
</script> 



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE)
```


```{r libraries}
library(readxl)
library(dplyr)
library(knitr)
library(timevis)

```

<br>
<br>
<br>

  
# 🍴Chosen Restaurants 

## 28th September -  El Pimiento Verde - Castelló  {.tabset .tabset-fade}

Booked 28th September, 2019
32 pax

<iframe src="EL PIMIENTO VERDE/ElPimientoVerde.html" frameborder="0" width="100%" height="1000" scrolling="no"></iframe>

### MENU 1

    ALL TO SHARE MENU
    Artichoke Flowers (2ud)
    Homemade creamy croquettes (2ud)
    (Iberian ham with parmesan + baby squid with ink)
    Warm angula, clam and prawn salad
    Navarra chistorra with creamy potatoes
    
    Seafood rice with clams, mussels and fresh fish
    
    Assortment of artisanal dessert and house coffee
    
    Red (Rioja Crianza) or white wine (Rueda Verdejo) (1 bottle each 3 pax) 
    and water.
  

    *Rates per person: 50€ VAT inc
    

<br>

### MENU 2

    ALL TO SHARE MENU
    Artichoke Flowers (2ud)
    Homemade creamy croquettes (2ud)
    (Iberian ham with parmesan + baby squid with ink)
    Homemade salad with piquillo peppers and tuna belly
    Navarra chistorra with creamy potatoes
    
    Cantabrian hake medallions with Bilbao-style babysquid and angula sauce
    
    Sliced Iberian pork "pluma" with cabrales cheese saucem fried potatoes and tomato and pepper tartare.
    
    Assortment of artisanal dessert and house coffee
    
    Red (Rioja Crianza) white wine (Rueda Verdejo) (1 bottle each 3 pax) 
    and water.
  
    *Rates per person: 56,50€ VAT inc
  

<br>

### MENU 3

    ALL TO SHARE MENU
    Artichoke Flowers (2ud)
    Homemade creamy croquettes (2ud)
    (Iberian ham with parmesan + baby squid with ink)
    Warm Cantabrian Salad (Mix of tender greens with sauteed angulas, clams and prawns)
    Fresh baby squid with Onions(Toasted on tasty piperrada)
    
    Cantabrian monkfish with Bilbao-style sauté (fillet of monkfish tripe with sautéed potato slices and broccolini)
    
    Grilled avileña-black iberian aged ribeye beef chop (Fillet cooked to desired doneness. With side of piquillo pepper and potatoes)
    
    Assortment of artisanal dessert and house coffee
    
    Red (Rioja Crianza) white wine (Rueda Verdejo) (1 bottle each 3 pax) 
    and water.
  

    *Rates per person: 62,50€ VAT inc
    *You will need to add 3€ if you want to include coffee.

<br>



## 30th September - Sinsombrero {.tabset .tabset-fade}

Booked 30th September, 2019
32pax

<iframe src="SINSOMBRERO/Sinsombrero.html" frameborder="0" width="100%" height="1000" scrolling="no"></iframe>


### MENU 1

    Starters to share
    Russian salad with tuna
    Iberic ham croquettes
    Special pizza of picanha, red pesto, arugula and stracciatela.

    Main course to choose
    Roasted salmon with miso
    or
    Ox burguer with cheese and glazed shallots

    Dessert
    Chocolate cke with maracuya soup, crunchy honey and cookie ice cream.

    *Rates per person: 37€ VAT inc
     + 3€ if you want to add coffee

    Drink package option 1 - 12€

    - 3 drinks (glass of wine, beer, water or soft drink)

    Drink package option2 - 20€

    - 2h open bar (wine, beer, juices, water and soft drinks)



### MENU 2

    Starters to share
    Russian salad with tuna
    Iberic ham croquettes
    Cuttlefish friters with lime mayonnaise

    Main course to choose
    Hake with green sauce of basil, shrimps and potato
    or
    Beef sirloin with garnish

    Dessert
    Chocolate cke with maracuya soup, crunchy honey and cookie ice cream.
    or
    Cheese ckae with red fruit ice-cream

    *Rates per person: 44€ VAT inc
     + 3€ if you want to add coffee

    Drink package option 1 - 12€

    - 3 drinks (glass of wine, beer, water or soft drink)

    Drink package option2 - 20€

    - 2h open bar (wine, beer, juices, water and soft drinks)



## 🚌 Bus Transfers & Assistance

  * 50 seater bus transfer from Madrid's Airport to NH Colon (or viceversa) (from 8.00h to 20.00h): 190€ VAT inc
  * 50 seater bus transfer from Madrid's Airport to NH Colon (or viceversa) (from 20.00h to 8.00h): 220€ VAT inc
  * 50 seater bus at disposal for dinner: 380€ VAT inc
  
  * English speaking assistant (2h) - 120€ VAT inc
  


*****

##  ☑ Terms & Conditions

  * Rates valid for 2019.
  
  * Net rates for Business travel
  
  * Cutting Edge Events management fee including in the detailed rates
  
  * VAT included. 
  
  
*****





